---
title: "MARVEL_Notebook for 6 samples MSS"
output: html_notebook
---


```{r}
#load MARVEL packages
library(Seurat)
library(MARVEL)
# loa adjunct packages for selected MARVEL  features 
# General data processing, plotting
library(ggnewscale)
library(ggrepel)
library(reshape2)
library(plyr)
library(stringr)
library(textclean)
```
```{r}
# Gene ontology analysis

library(AnnotationDbi)
library(clusterProfiler)
library(org.Hs.eg.db)
library(org.Mm.eg.db)
```
```{r}
# ad hoc gene candidate gene analysis
library(gtools)
```
```{r}
# Visualising splice junction location
library(GenomicRanges)
library(IRanges)
library(S4Vectors)
library(wiggleplotr)
```
```{r}

library(Matrix)
library(data.table)
library(ggplot2)
library(gridExtra)
```

```{r}
library(usethis)
library(devtools)
```



```{r}
# Matrix
path <- "~/Desktop/stage_M2/integrate_marvel/MARVEL_input/Gene_SingCellaR_MSS/"
file <- "matrix_normalised.mtx"
df.gene.norm <- readMM(paste(path, file, sep=""))

df.gene.norm[df.gene.norm[,1] !=0,][1:5,1:5]
```
```{r}
# cell metadata
path <- "~/Desktop/stage_M2/integrate_marvel/MARVEL_input/Gene_SingCellaR_MSS/"
file <- "phenoData.txt"
df.gene.norm.pheno <- read.table(paste(path, file, sep=""), sep="\t", header=TRUE, stringsAsFactors=FALSE)

head(df.gene.norm.pheno)
```


```{r}
# gene metadata
path <- "~/Desktop/stage_M2/integrate_marvel/MARVEL_input/Gene_SingCellaR_MSS/"
file <- "featureData.txt"
df.gene.norm.feature <- read.table(paste(path, file, sep=""), sep="\t", header=TRUE, stringsAsFactors=FALSE)

head(df.gene.norm.feature)

```
```{r}
#Gene counts
# Matrix
path <- "~/Desktop/stage_M2/integrate_marvel/MARVEL_input/Gene_STARsolo_MSS/"
file <- "matrix_counts.mtx"
df.gene.count <- readMM(paste(path, file, sep=""))

df.gene.count[df.gene.count[,1] !=0,][1:5,1:5]

```
```{r}
# cell metadata
path <- "~/Desktop/stage_M2/integrate_marvel/MARVEL_input/Gene_STARsolo_MSS/"
file <- "phenoData.txt"
df.gene.count.pheno <- read.table(paste(path, file, sep=""), sep="\t", header=TRUE, stringsAsFactors=FALSE)

head(df.gene.count.pheno)
```
```{r}
# feature metadata
path <- "~/Desktop/stage_M2/integrate_marvel/MARVEL_input/Gene_STARsolo_MSS/"
file <- "featureData.txt"
df.gene.count.feature <- read.table(paste(path, file, sep=""), sep="\t", header=TRUE, stringsAsFactors=FALSE)

head(df.gene.count.feature)
```

#Splice junction counts
## Matrix
```{r}

path <- "~/Desktop/stage_M2/integrate_marvel/MARVEL_input/SJ_STARsolo_MSS/"
file <- "matrix_counts.mtx"
df.sj.count <- readMM(paste(path, file, sep=""))
df.sj.count   #[df.sj.count[,1] !=0,][1:5,1:5]

```


```{r}
# cell metadata
path <- "~/Desktop/stage_M2/integrate_marvel/MARVEL_input/SJ_STARsolo_MSS/"
file <- "phenoData.txt"
df.sj.count.pheno <- read.table(paste(path, file, sep=""), sep="\t", header=TRUE, stringsAsFactors=FALSE)

df.sj.count.pheno

```
```{r}
# feature metadata
path <- "~/Desktop/stage_M2/integrate_marvel/MARVEL_input/SJ_STARsolo_MSS/"
file <- "featureData.txt"
df.sj.count.feature <- read.table(paste(path, file, sep=""), sep="\t", header=TRUE, stringsAsFactors=FALSE)

head(df.sj.count.feature)

```

```{r}
#tSNE/UMAP coordinates
path <- "~/Desktop/stage_M2/integrate_marvel/SingCellaR_output/"
file <- "dim_red_coordinates_MSS.txt"
df.coord <- read.table(paste(path, file, sep=""), sep="\t", header=TRUE, stringsAsFactors=FALSE)

df.coord

```
##Gene transfer file
   For consistency, this GTF should be the same file previously used for cellranger and STARsolo above.
```{r}
path <- "/home/assanefall/yard/run_cellranger_count/refdata-gex-GRCh38-2020-A/genes/"
file <- "genes.gtf"
gtf <- as.data.frame(fread(paste(path, file, sep=""), sep="\t", header=FALSE, stringsAsFactors=FALSE))
gtf$V9 = gsub("gene_type","gene_biotype",gtf$V9)
gtf$V9 = gsub("transcript_type","transcript_biotype",gtf$V9)
gtf$V1 = gsub("chr","",gtf$V1)
head(gtf)
```
```{r}
#Create MARVEL object
marvel <- CreateMarvelObject.10x(gene.norm.matrix=df.gene.norm,
                                 gene.norm.pheno=df.gene.norm.pheno,
                                 gene.norm.feature=df.gene.norm.feature,
                                 gene.count.matrix=df.gene.count,
                                 gene.count.pheno=df.gene.count.pheno,
                                 gene.count.feature=df.gene.count.feature,
                                 sj.count.matrix=df.sj.count,
                                 sj.count.pheno=df.sj.count.pheno,
                                 sj.count.feature=df.sj.count.feature,
                                 pca=df.coord,
                                 gtf=gtf
                                 )
```
```{r}
"Pre-process data
             This step annotates the gene and splice junction metadata, and subsequently enables us to retain only high-quality splice junctions and genes of particular biotype, e.g., protein-coding genes.
             
Annotate gene metadata
             This step annotates the genes with their corresponding gene biotype, e.g., protein-coding, lincRNA, pseudogene etc."

marvel <- AnnotateGenes.10x(MarvelObject=marvel)
head(marvel$gene.metadata)
```


```{r}
table(marvel$gene.metadata$gene_type)
```
```{r}
  " This step creates and then annotates the splice junction metadata. For each splice junction, the start and end exons are annotated with their corresponding gene names.

Annotate junction metadata"

marvel <- AnnotateSJ.10x(MarvelObject=marvel)

head(marvel$sj.metadata)
```
```{r}
"Validate junctions
             Only splice junctions whose start and end mapped to same gene are retained."
marvel <- ValidateSJ.10x(MarvelObject=marvel)
```
```{r}
"Subset CDS genes
             Moving forward, we will only retain genes with coding sequence (CDS), i.e., protein-coding genes."

marvel <- FilterGenes.10x(MarvelObject=marvel,
                          gene.type="protein_coding"
                          )
```

```{r}
marvel <- CheckAlignment.10x(MarvelObject=marvel)
```


#ANNOTATION CENSUS


```{r}
load(file = "/home/assanefall/Desktop/stage_M2/integrate_marvel/annotation_Census_MSS.rdata")
```
## subset
```{r}
marvel_mss = Subset_marvel(marvel,res_MSS$pred$barcode)
```


#### subset : cancer cells
```{r}
df1 = as.data.frame(marvel_mss$sample.metadata)
df2 = as.data.frame(res_MSS$pred)
cell = merge(df2, df1, by.x = 'barcode', by.y='cell.id')

```

# ```{r}
# lll = marvel_mss$sample.metadata$cell.type[marvel_mss$sample.metadata$cell.type=="cancer cell"]
# ```
# ```{r}
# marvel_cc = Subset_marvel(marvel_mss,lll)
# ```
```{r}
#marvel_mss$sample.metadata$cell.type <- cell$celltype
```

```{r}
table(marvel_mss$sample.metadata$cell.type)
```
```{r}
length(marvel_mss$sample.metadata$cell.type)
```

```{r}
mss_ids <- c(
  "SRR15653121",
  "SRR15653122",
  "SRR15653116",
  "SRR15653117",
  "SRR15653024",
  "SRR15653120"
)

for (id in mss_ids) {
  marvel_mss$sample.metadata$status[
    grepl(id, marvel_mss$sample.metadata$cell.id)
  ] <- "MSS"
}

```

Explore expression

          
```{r}
table(marvel_mss$sample.metadata$donor.id)

```
             
             
             
Gene expression rate
# Define cell groups
  # Retrieve sample metadata
```{r}

sample.metadata <- marvel_mss$sample.metadata

# Group 1 (reference)
index <- which(sample.metadata$cell.type=="TA")
cell.ids.1 <- sample.metadata[index, "cell.id"]
length(cell.ids.1)

```
```{r}
 # Group 2
index <- which(sample.metadata$cell.type=="Colonocyte")
cell.ids.2 <- sample.metadata[index, "cell.id"]
length(cell.ids.2)
```
```{r}
# Explore % of cells expressing genes
marvel_mss <- PlotPctExprCells.Genes.10x(MarvelObject=marvel_mss,
                                     cell.group.g1=cell.ids.1,
                                     cell.group.g2=cell.ids.2,
                                     min.pct.cells=5
                                     )
marvel_mss$pct.cells.expr$Gene$Plot
```


```{r}
head(marvel_mss$pct.cells.expr$Gene$Data)
```
```{r}

    "_min.pct.cells option. The minimum percentage of cells expressing a given gene for that gene to be included for expression exploration analysis here.
    
    _Here, we observe majority of genes to be expressed in ~10% of cells.

SJ expression rate"

marvel_mss <- PlotPctExprCells.SJ.10x(MarvelObject=marvel_mss,
                                  cell.group.g1=cell.ids.1,
                                  cell.group.g2=cell.ids.2,
                                  min.pct.cells.genes=5,
                                  min.pct.cells.sj=5,
                                  downsample=TRUE,
                                  downsample.pct.sj=10
                                  )

marvel_mss$pct.cells.expr$SJ$Plot
```
```{r}
head(marvel_mss$pct.cells.expr$SJ$Data)
```
```{r}
"Differential analysis"

"L'analyse différentielle est la pierre angulaire de l'analyse de séquençage d'ARN. Il s'agit de la première étape pour identifier les gènes candidats et les isoformes pour la validation expérimentale en aval.

  Pour l'analyse d'épissage différentiel, MARVEL utilise l'approche basée sur la permutation pour comparer les valeurs PSI entre deux échantillons pseudo-globaux"

```
```{r}
#Differential splicing analysis

marvel_mss <- CompareValues.SJ.10x(MarvelObject=marvel_mss,
                               cell.group.g1=cell.ids.1,
                               cell.group.g2=cell.ids.2,
                               min.pct.cells.genes=10,
                               min.pct.cells.sj=10,
                               min.gene.norm=1.0,
                               seed=1,
                               n.iterations=100,
                               downsample=TRUE,
                               show.progress=FALSE
                               )
```
```{r}
#Differential gene analysis

marvel_mss <- CompareValues.Genes.10x(MarvelObject=marvel_mss,
                                  show.progress=FALSE
                                  )

head(marvel_mss$DE$SJ$Table)
```
```{r}
#Volcano plot: Splicing
marvel_mss <- PlotDEValues.SJ.10x(MarvelObject=marvel_mss,
                              pval=0.05,
                              delta=5,
                              min.gene.norm=1.0,
                              anno=FALSE
                              )

marvel_mss$DE$SJ$VolcanoPlot$SJ$Plot
```
```{r}
head(marvel_mss$DE$SJ$VolcanoPlot$SJ$Data[,c("coord.intron", "gene_short_name", "sig")])
```
```{r}
#Gene-splicing dynamics

#Assign dynamics

marvel_mss <- IsoSwitch.10x(MarvelObject=marvel_mss,
                        pval.sj=0.05,
                        delta.sj=5,
                        min.gene.norm=1.0,
                        pval.adj.gene=0.05,
                        log2fc.gene=0.5
                        )

marvel_mss$SJ.Gene.Cor$Proportion$Plot
```
```{r}
marvel_mss$SJ.Gene.Cor$Proportion$Table
```
```{r}
head(marvel_mss$SJ.Gene.Cor$Data[,c("coord.intron", "gene_short_name", "cor.complete")])
```
```{r}
#Coordinated
# Define cell groups
    # Retrieve sample metadata
    sample.metadata <- marvel_mss$sample.metadata
    
    # MSS
    index <- which(sample.metadata$cell.type=="TA")
    cell.ids.1 <- sample.metadata[index, "cell.id"]
    length(cell.ids.1)
```

```{r}
    # MSI
    index <- which(sample.metadata$cell.type=="Colonocyte")
    cell.ids.2 <- sample.metadata[index, "cell.id"]
    length(cell.ids.2)
```
```{r}
# Save into list
    cell.group.list <- list("TA"=cell.ids.1,
                            "Colonocytes"=cell.ids.2
                            )
    
# Plot cell groups
marvel_mss <- PlotValues.PCA.CellGroup.10x(MarvelObject=marvel_mss,
                                       cell.group.list=cell.group.list,
                                       legendtitle="Cell group",
                                       type="tsne"
                                       )

plot_group <- marvel_mss$adhocPlot$PCA$CellGroup

# Plot gene expression
marvel_mss <- PlotValues.PCA.Gene.10x(MarvelObject=marvel_mss,
                                  gene_short_name="VIM",
                                  color.gradient=c("grey","cyan","green","yellow","red"),
                                  type="tsne"
                                  )


plot_gene <- marvel_mss$adhocPlot$PCA$Gene

# Plot PSI
marvel_mss <- PlotValues.PCA.PSI.10x(MarvelObject=marvel_mss,
                                 coord.intron="chr10:17235390:17235845",
                                 min.gene.count=3,
                                 log2.transform=FALSE,
                                 color.gradient=c("grey","cyan","green","yellow","red"),
                                 type="tsne"
                                 )
 
plot_sj <- marvel_mss$adhocPlot$PCA$PSI

# Arrange and view plots
grid.arrange(plot_group, plot_gene, plot_sj, nrow=1)
```
```{r}
#Opposing

# Plot gene expression
marvel_mss <- PlotValues.PCA.Gene.10x(MarvelObject=marvel_mss,
                                  gene_short_name="UQCRH",
                                  color.gradient=c("grey","cyan","green","yellow","red"),
                                  type="tsne"
                                  )


plot_gene <- marvel_mss$adhocPlot$PCA$Gene

# Plot PSI
marvel_mss <- PlotValues.PCA.PSI.10x(MarvelObject=marvel_mss,
                                 coord.intron="chr1:46310317:46316551",
                                 min.gene.count=3,
                                 log2.transform=FALSE,
                                 color.gradient=c("grey","cyan","green","yellow","red"),
                                 type="tsne"
                                 )
 
plot_sj <- marvel_mss$adhocPlot$PCA$PSI

# Arrange and view plots
grid.arrange(plot_group, plot_gene, plot_sj, nrow=1)
```
```{r}
#Iso-switch

# Plot gene expression
marvel_mss <- PlotValues.PCA.Gene.10x(MarvelObject=marvel_mss,
                                  gene_short_name="RBM39",
                                  color.gradient=c("grey","cyan","green","yellow","red"),
                                  type="tsne"
                                  )


plot_gene <- marvel_mss$adhocPlot$PCA$Gene

# Plot PSI: SJ-1
marvel_mss <- PlotValues.PCA.PSI.10x(MarvelObject=marvel_mss,
                                 coord.intron="chr20:35740888:35741940",
                                 min.gene.count=3,
                                 log2.transform=FALSE,
                                 color.gradient=c("grey","cyan","green","yellow","red"),
                                 type="tsne"
                                 )
 
plot_sj_1 <- marvel_mss$adhocPlot$PCA$PSI

# Plot PSI: SJ-2
marvel_mss <- PlotValues.PCA.PSI.10x(MarvelObject=marvel_mss,
                                 coord.intron="chr20:35739018:35740823",
                                 min.gene.count=3,
                                 log2.transform=FALSE,
                                 color.gradient=c("grey","cyan","green","yellow","red"),
                                 type="tsne"
                                 )
 
plot_sj_2 <- marvel_mss$adhocPlot$PCA$PSI

# Arrange and view plots
grid.arrange(plot_gene, plot_sj_1, plot_sj_2, nrow=1)
```
```{r}
Complex

# Gene 1
  # Plot gene expression
  marvel_mss <- PlotValues.PCA.Gene.10x(MarvelObject=marvel_mss,
                                    gene_short_name="TPM1",
                                    color.gradient=c("grey","cyan","green","yellow","red"),
                                    type="tsne"
                                    )

  plot.1_gene <- marvel_mss$adhocPlot$PCA$Gene
  
  # Plot PSI: SJ-1
  marvel_mss <- PlotValues.PCA.PSI.10x(MarvelObject=marvel_mss,
                                   coord.intron="chr15:63064143:63065895",
                                   min.gene.count=3,
                                   log2.transform=FALSE,
                                   color.gradient=c("grey","cyan","green","yellow","red"),
                                   type="tsne"
                                   )
   
  plot.1_sj_1 <- marvel_mss$adhocPlot$PCA$PSI
  
  # Plot PSI: SJ-2
  marvel_mss <- PlotValues.PCA.PSI.10x(MarvelObject=marvel_mss,
                                   coord.intron="chr15:63044153:63056984",
                                   min.gene.count=3,
                                   log2.transform=FALSE,
                                   color.gradient=c("grey","cyan","green","yellow","red"),
                                   type="tsne"
                                   )
   
  plot.1_sj_2 <- marvel_mss$adhocPlot$PCA$PSI

# Gene 2
  # Plot gene expression
  marvel_mss <- PlotValues.PCA.Gene.10x(MarvelObject=marvel_mss,
                                    gene_short_name="TPM2",
                                    color.gradient=c("grey","cyan","green","yellow","red"),
                                    type="tsne"
                                    )
  
  
  plot.2_gene <- marvel_mss$adhocPlot$PCA$Gene
  
  # Plot PSI: SJ-1
  marvel_mss <- PlotValues.PCA.PSI.10x(MarvelObject=marvel_mss,
                                   coord.intron="chr9:35684808:35685268",
                                   min.gene.count=3,
                                   log2.transform=FALSE,
                                   color.gradient=c("grey","cyan","green","yellow","red"),
                                   type="tsne"
                                   )
   
  plot.2_sj_1 <- marvel_mss$adhocPlot$PCA$PSI
  
  # Plot PSI: SJ-2
  marvel_mss <- PlotValues.PCA.PSI.10x(MarvelObject=marvel_mss,
                                   coord.intron="chr9:35684551:35685063",
                                   min.gene.count=3,
                                   log2.transform=FALSE,
                                   color.gradient=c("grey","cyan","green","yellow","red"),
                                   type="tsne"
                                   )
   
  plot.2_sj_2 <- marvel_mss$adhocPlot$PCA$PSI
  
# Arrange and view plots
grid.arrange(plot.1_gene, plot.1_sj_1, plot.1_sj_2, 
             plot.2_gene, plot.2_sj_1, plot.2_sj_2,
             nrow=2
             )
```

##Gene ontology analysis
             Gene ontology analysis or pathway enrichment analysis categorises the differentially spliced genes between cancer cells and the others into biological pathways. This may identify sets of genes with similar function or belong to similar biological pathways that are concurrently spliced.
```{r}


marvel_mss <- BioPathways.10x(MarvelObject=marvel_mss,
                          pval=0.05,
                          delta=5,
                          min.gene.norm=1.0,
                          method.adjust="fdr",
                          species="human"
                          )

head(marvel_mss$DE$BioPathways$Table)
```
# Plot pathways
```{r}

go.terms <- c("ATP metabolic process",
              "mitochondrial respiratory chain complex assembly",
              "aerobic respiration",
              "ribose phosphate biosynthetic process",
              "RNA splicing",
              "reactive oxygen species metabolic process",
              "response to mitochondrial depolarisation",
              "intracellular protein transmembrane transport",
              "U2-type prespliceosome assembly",
              "regulation of cell communication by electrical coupling",
              "response to zinc ion"
              )

marvel_mss <- BioPathways.Plot.10x(MarvelObject=marvel_mss,
                               go.terms,
                               y.label.size=8,
                               offset=0.5
                               )

marvel_mss$DE$BioPathways$Plot
```
#Candidate gene analysis

####Define cell groups
  "Our earlier differential analysis included only MSS and MSI. Here, we will include all cell types in this dataset, namely TA, Colonocytes, Stem cells and Enterocytes.
"
# Retrieve sample metadata
## TA
```{r}

sample.metadata <- marvel_mss$sample.metadata

index <- which(sample.metadata$cell.type=="TA")
cell.ids.1 <- sample.metadata[index, "cell.id"]
length(cell.ids.1)

```
## Coloncoyte
```{r}

index <- which(sample.metadata$cell.type=="Colonocyte")
cell.ids.2 <- sample.metadata[index, "cell.id"]
length(cell.ids.2)
```
### Stem cells
```{r}

index <- which(sample.metadata$cell.type=="Stem cells")
cell.ids.3 <- sample.metadata[index, "cell.id"]
length(cell.ids.3)
```
## Enterocyte
```{r}
index <- which(sample.metadata$cell.type=="Enterocyte")
cell.ids.4 <- sample.metadata[index, "cell.id"]
length(cell.ids.4)
```
```{r}
# Save into list
cell.group.list <- list("TA"=cell.ids.1,
                        "Colonocyte"=cell.ids.2,
                        "Stem cells"=cell.ids.3,
                        "Enterocyte"=cell.ids.4
                        )
```
#Gene expression profiling
```{r}


marvel <- adhocGene.TabulateExpression.Gene.10x(MarvelObject=marvel,
                                                cell.group.list=cell.group.list,
                                                gene_short_name="SPARC",
                                                min.pct.cells=10,
                                                downsample=TRUE
                                                )

marvel$adhocGene$Expression$Gene$Plot
```
```{r}
marvel$adhocGene$Expression$Gene$Table
```
#SJ usage profiling
```{r}


marvel_mss <- adhocGene.TabulateExpression.PSI.10x(MarvelObject=marvel_mss,
                                               min.pct.cells=10
                                               )

marvel_mss$adhocGene$Expression$PSI$Plot


```
```{r}
head(marvel$adhocGene$Expression$PSI$Table)
```
"Gene-splicing relationship

    Let’s investigate how the top 3 most highly-expressed splice junctions’ usage (SJ-1, -2, and -3) changes relative to TPM2 gene expression changes for all possible pair-wise comparison between iPSCs, and day-2, -4, and -10 cardiomyocytes."

# Perform differential gene expression analysis for all pair-wise group comparison
```{r}
marvel_mss <- adhocGene.DE.Gene.10x(MarvelObject=marvel_mss)
```
# Perform differential splicing expression analysis for all pair-wise group comparison

```{r}
marvel <- adhocGene.DE.PSI.10x(MarvelObject=marvel)
```

# Retrieve SJ DE results table
```{r}

results <- marvel$adhocGene$DE$PSI$Data

# SJ-1
  # Define SJ
  coord.intron <- results[which(results$figure.column=="SJ-1"), "coord.intron"]
  coord.intron <- unique(coord.intron)
  coord.intron
```
```{r}
  # Plot
  marvel <- adhocGene.PlotDEValues.10x(MarvelObject=marvel,
                                       coord.intron=coord.intron,
                                       log2fc.gene=0.5,
                                       delta.sj=5,
                                       label.size=2,
                                       point.size=2,
                                       xmin=-2.0,
                                       xmax=2.0,
                                       ymin=-25,
                                       ymax=25
                                       )

  plot.1 <- marvel$adhocGene$DE$VolcanoPlot$Plot

# SJ-2
  # Define SJ
  coord.intron <- results[which(results$figure.column=="SJ-2"), "coord.intron"]
  coord.intron <- unique(coord.intron)
  coord.intron
```
```{r}
  # Plot
  marvel <- adhocGene.PlotDEValues.10x(MarvelObject=marvel,
                                       coord.intron=coord.intron,
                                       log2fc.gene=0.5,
                                       delta.sj=5,
                                       label.size=2,
                                       point.size=2,
                                       xmin=-2.0,
                                       xmax=2.0,
                                       ymin=-25,
                                       ymax=25
                                       )
                                         
  plot.2 <- marvel$adhocGene$DE$VolcanoPlot$Plot    

# SJ-3
    # Define SJ
    coord.intron <- results[which(results$figure.column=="SJ-3"), "coord.intron"]
    coord.intron <- unique(coord.intron)
    coord.intron
```
```{r}
    # Plot
    marvel <- adhocGene.PlotDEValues.10x(MarvelObject=marvel,
                                         coord.intron=coord.intron,
                                         log2fc.gene=0.5,
                                         delta.sj=5,
                                         label.size=2,
                                         point.size=2,
                                         xmin=-2.0,
                                         xmax=2.0,
                                         ymin=-25,
                                         ymax=25
                                         )
                                         
    plot.3 <- marvel$adhocGene$DE$VolcanoPlot$Plot    

# Arrange and view plots
grid.arrange(plot.1, plot.2, plot.3,
             nrow=3
             )
```
```{r}
library(wiggleplotr)
#Locate SJ position
  "Locating the position of the splice junctions on the isoforms corresponding to TPM2 will reveal the specific isoforms expressed in our dataset for this."

# SJ-1
    # Define SJs to plot
    coord.intron <- results[which(results$figure.column=="SJ-1"), "coord.intron"]
    coord.intron <- unique(coord.intron)
    coord.intron
```
```{r}
 # Plot
marvel <- adhocGene.PlotSJPosition.10x(MarvelObject=marvel,
                                      coord.intron=coord.intron,
                                      rescale_introns=FALSE,
                                      show.protein.coding.only=TRUE,
                                      anno.label.size=1.5
                                      )

marvel$adhocGene$SJPosition$Plot
  
```
```{r}
# SJ-2
    # Define SJs to plot
    coord.intron <- results[which(results$figure.column=="SJ-2"), "coord.intron"]
    coord.intron <- unique(coord.intron)
    coord.intron
```
```{r}
# Plot
    marvel <- adhocGene.PlotSJPosition.10x(MarvelObject=marvel,
                                          coord.intron=coord.intron,
                                          rescale_introns=FALSE,
                                          show.protein.coding.only=TRUE,
                                          anno.label.size=1.5
                                          )
    
    marvel$adhocGene$SJPosition$Plot
```
