---
title: "MARVEL_Notebook for Integrating MSS and MSI Samples"
output: html_notebook
---


```{r}
#load MARVEL packages
library(Seurat)
library(MARVEL)
# loa adjunct packages for selected MARVEL  features 
# General data processing, plotting
library(ggnewscale)
library(ggrepel)
library(reshape2)
library(plyr)
library(stringr)
library(textclean)
```
```{r}
# Gene ontology analysis

library(AnnotationDbi)
library(clusterProfiler)
library(org.Hs.eg.db)
library(org.Mm.eg.db)
```
```{r}
# ad hoc gene candidate gene analysis
library(gtools)
```
```{r}
# Visualising splice junction location
library(GenomicRanges)
library(IRanges)
library(S4Vectors)
library(wiggleplotr)
```
```{r}
# Load adjunct packages for this tutorial
library(Matrix)
library(data.table)
library(ggplot2)
library(gridExtra)
```

```{r}
library(usethis)
library(devtools)
```


####  Gene expression (normalized matrix) data for integ
```{r}
# Matrix
path <- "~/Desktop/stage_M2/integrate_marvel/MARVEL_input/Gene_SingCellaR_mix/"
file <- "matrix_normalised.mtx"
df.gene.norm <- readMM(paste(path, file, sep=""))

df.gene.norm[df.gene.norm[,1] !=0,][1:5,1:5]
```
###  Cell metadata (Gene_SingCellaR)
```{r}
# cell metadata
path <- "~/Desktop/stage_M2/integrate_marvel/MARVEL_input/Gene_SingCellaR_mix/"
file <- "phenoData.txt"
df.gene.norm.pheno <- read.table(paste(path, file, sep=""), sep="\t", header=TRUE, stringsAsFactors=FALSE)

head(df.gene.norm.pheno)
```

### Gene features (names/IDs)
```{r}
# gene metadata
path <- "~/Desktop/stage_M2/integrate_marvel/MARVEL_input/Gene_SingCellaR_mix/"
file <- "featureData.txt"
df.gene.norm.feature <- read.table(paste(path, file, sep=""), sep="\t", header=TRUE, stringsAsFactors=FALSE)

head(df.gene.norm.feature)

```

# Gene counts (STARsolo)
```{r}
#Gene counts
# Matrix
path <- "~/Desktop/stage_M2/integrate_marvel/MARVEL_input/Gene_STARsolo_mix/"
file <- "matrix_counts.mtx"
df.gene.count <- readMM(paste(path, file, sep=""))

df.gene.count[df.gene.count[,1] !=0,][1:5,1:5]

```

### Cell metadata (Gene_STARsolo)
```{r}
# cell metadata
path <- "~/Desktop/stage_M2/integrate_marvel/MARVEL_input/Gene_STARsolo_mix/"
file <- "phenoData.txt"
df.gene.count.pheno <- read.table(paste(path, file, sep=""), sep="\t", header=TRUE, stringsAsFactors=FALSE)

head(df.gene.count.pheno)
```

### Gene features (STARsolo)

```{r}
# feature metadata
path <- "~/Desktop/stage_M2/integrate_marvel/MARVEL_input/Gene_STARsolo_mix/"
file <- "featureData.txt"
df.gene.count.feature <- read.table(paste(path, file, sep=""), sep="\t", header=TRUE, stringsAsFactors=FALSE)

head(df.gene.count.feature)
```

### Splice junction counts Matrix
```{r}

path <- "~/Desktop/stage_M2/integrate_marvel/MARVEL_input/SJ_STARsolo_mix/"
file <- "matrix_counts.mtx"
df.sj.count <- readMM(paste(path, file, sep=""))
df.sj.count   #[df.sj.count[,1] !=0,][1:5,1:5]

```
### Cell metadata (SJ_STARsolo)

```{r}
# cell metadata
path <- "~/Desktop/stage_M2/integrate_marvel/MARVEL_input/SJ_STARsolo_mix/"
file <- "phenoData.txt"
df.sj.count.pheno <- read.table(paste(path, file, sep=""), sep="\t", header=TRUE, stringsAsFactors=FALSE)

head(df.sj.count.pheno)

```

### Junction features
```{r}
# feature metadata
path <- "~/Desktop/stage_M2/integrate_marvel/MARVEL_input/SJ_STARsolo_mix/"
file <- "featureData.txt"
df.sj.count.feature <- read.table(paste(path, file, sep=""), sep="\t", header=TRUE, stringsAsFactors=FALSE)

head(df.sj.count.feature)

```

#### tSNE/UMAP coordinates
```{r}

path <- "~/Desktop/stage_M2/integrate_marvel/SingCellaR_output/"
file <- "dim_red_coordinates_mix.txt"
df.coord <- read.table(paste(path, file, sep=""), sep="\t", header=TRUE, stringsAsFactors=FALSE)

head(df.coord)

```
#### Gene transfer file (common to CellRanger/STARsolo)
   For consistency, this GTF should be the same file previously used for cellranger and STARsolo above.
```{r}
path <- "/home/assanefall/yard/run_cellranger_count/refdata-gex-GRCh38-2020-A/genes/"
file <- "genes.gtf"
gtf <- as.data.frame(fread(paste(path, file, sep=""), sep="\t", header=FALSE, stringsAsFactors=FALSE))
gtf$V9 = gsub("gene_type","gene_biotype",gtf$V9)
gtf$V9 = gsub("transcript_type","transcript_biotype",gtf$V9)
gtf$V1 = gsub("chr","",gtf$V1)
head(gtf)
```

### Create MARVEL object global
```{r}

marvel <- CreateMarvelObject.10x(gene.norm.matrix=df.gene.norm,
                                 gene.norm.pheno=df.gene.norm.pheno,
                                 gene.norm.feature=df.gene.norm.feature,
                                 gene.count.matrix=df.gene.count,
                                 gene.count.pheno=df.gene.count.pheno,
                                 gene.count.feature=df.gene.count.feature,
                                 sj.count.matrix=df.sj.count,
                                 sj.count.pheno=df.sj.count.pheno,
                                 sj.count.feature=df.sj.count.feature,
                                 pca=df.coord,
                                 gtf=gtf
                                 )
```


```{r}
"Pre-process data
             This step annotates the gene and splice junction metadata, and subsequently enables us to retain only high-quality splice junctions and genes of particular biotype, e.g., protein-coding genes.
             
Annotate gene metadata
             This step annotates the genes with their corresponding gene biotype, e.g., protein-coding, lincRNA, pseudogene etc."

marvel <- AnnotateGenes.10x(MarvelObject=marvel)
head(marvel$gene.metadata)
```


```{r}
table(marvel$gene.metadata$gene_type)
```
```{r}
  " This step creates and then annotates the splice junction metadata. For each splice junction, the start and end exons are annotated with their corresponding gene names.

Annotate junction metadata"

marvel <- AnnotateSJ.10x(MarvelObject=marvel)

head(marvel$sj.metadata)
```
```{r}
"Validate junctions
             Only splice junctions whose start and end mapped to same gene are retained."
marvel <- ValidateSJ.10x(MarvelObject=marvel)
```
```{r}
"Subset CDS genes
             Moving forward, we will only retain genes with coding sequence (CDS), i.e., protein-coding genes."

marvel <- FilterGenes.10x(MarvelObject=marvel,
                          gene.type="protein_coding"
                          )
```

```{r}
marvel <- CheckAlignment.10x(MarvelObject=marvel)
```


#ANNOTATION CENSUS


```{r}
load(file = '~/Desktop/stage_M2/integrate_marvel/annotation_Census_mix.rdata')
```
## subset
```{r}
marvel_subset = Subset_marvel(marvel,res_mix$pred$barcode)
```
#### subset : cancer cells

# ```{r}
# lll = marvel_subset$sample.metadata$cell.type[marvel_subset$sample.metadata$cell.type=="cancer cell"]
# ```
# ```{r}
# marvel_cc = Subset_marvel(marvel_subset,lll)
# ```
```{r}
marvel_subset$sample.metadata$cell.type <- res_mix$pred$celltype
```


```{r}

marvel_subset$sample.metadata$status <- NA

# Dictionnaire SRR → statut
status_map <- list(
  "MSI" = c(
    "SRR15652857", "SRR15652858", "SRR15652897",
    "SRR15652970", "SRR15652975",
    "SRR15652896", "SRR15652861", "SRR15652900",
    "SRR15652844", "SRR15652845", "SRR15652846", "SRR15652847",
    "SRR15652867", "SRR15652868", "SRR15652869", "SRR15652870",
    "SRR15652862", "SRR15652859"
  ),
  "MSS" = c(
    "SRR15653116",
    "SRR15653121", "SRR15653122",
    "SRR15653024"
  )
)

# Attribuer status pour chaque type
for (stat in names(status_map)) {
  ids <- status_map[[stat]]
  for (id in ids) {
    marvel_subset$sample.metadata$status[
      grepl(id, marvel_subset$sample.metadata$cell.id)
    ] <- stat
  }
}

```

Explore expression

             Due to the huge number of splice junctions detected, it will not be time-effective to include all splice junctions for differential splicing analysis. Therefore, we will only include splice junctions expressed in at least a user-defined proportion of cells for differential splicing analysis. To determine this threshold, we will explore the number of cells expressing a given gene and splice junction.
             We will explore the gene and splice junction expression rate in iPSCs and day-10 cardiomyocytes as we will be performing differential splicing analysis on these two cell populations.
```{r}
table(marvel_subset$sample.metadata$status)

```
             
             
             
Gene expression rate
# Define cell groups
  # Retrieve sample metadata
```{r}

sample.metadata <- marvel_subset$sample.metadata

# Group 1 (reference)
index <- which(sample.metadata$cell.type=="cancer cell")
cell.ids.1 <- sample.metadata[index, "cell.id"]
length(cell.ids.1)

```
```{r}
 # Group 2
index <- which(sample.metadata$cell.type=="immature enterocyte")
cell.ids.2 <- sample.metadata[index, "cell.id"]
length(cell.ids.2)
```
```{r}
# Explore % of cells expressing genes
marvel_subset <- PlotPctExprCells.Genes.10x(MarvelObject=marvel_subset,
                                     cell.group.g1=cell.ids.1,
                                     cell.group.g2=cell.ids.2,
                                     min.pct.cells=5
                                     )
marvel_subset$pct.cells.expr$Gene$Plot
```


```{r}
head(marvel_subset$pct.cells.expr$Gene$Data)
```
```{r}

    "_min.pct.cells option. The minimum percentage of cells expressing a given gene for that gene to be included for expression exploration analysis here.
    
    _Here, we observe majority of genes to be expressed in ~10% of cells.

SJ expression rate"

marvel_subset <- PlotPctExprCells.SJ.10x(MarvelObject=marvel_subset,
                                  cell.group.g1=cell.ids.1,
                                  cell.group.g2=cell.ids.2,
                                  min.pct.cells.genes=5,
                                  min.pct.cells.sj=5,
                                  downsample=TRUE,
                                  downsample.pct.sj=10
                                  )

marvel_subset$pct.cells.expr$SJ$Plot
```
```{r}
head(marvel_subset$pct.cells.expr$SJ$Data)
```
```{r}
"Differential analysis"

"L'analyse différentielle est la pierre angulaire de l'analyse de séquençage d'ARN. Il s'agit de la première étape pour identifier les gènes candidats et les isoformes pour la validation expérimentale en aval.

  Pour l'analyse d'épissage différentiel, MARVEL utilise l'approche basée sur la permutation pour comparer les valeurs PSI entre deux échantillons pseudo-globaux"

```
```{r}
#Differential splicing analysis

marvel_subset <- CompareValues.SJ.10x(MarvelObject=marvel_subset,
                               cell.group.g1=cell.ids.1,
                               cell.group.g2=cell.ids.2,
                               min.pct.cells.genes=10,
                               min.pct.cells.sj=10,
                               min.gene.norm=1.0,
                               seed=1,
                               n.iterations=100,
                               downsample=TRUE,
                               show.progress=FALSE
                               )
```
```{r}
#Differential gene analysis

marvel_subset <- CompareValues.Genes.10x(MarvelObject=marvel_subset,
                                  show.progress=FALSE
                                  )

head(marvel_subset$DE$SJ$Table)
```
```{r}
#Volcano plot: Splicing
marvel_subset <- PlotDEValues.SJ.10x(MarvelObject=marvel_subset,
                              pval=0.05,
                              delta=5,
                              min.gene.norm=1.0,
                              anno=FALSE
                              )

marvel_subset$DE$SJ$VolcanoPlot$SJ$Plot
```
```{r}
head(marvel_subset$DE$SJ$VolcanoPlot$SJ$Data[,c("coord.intron", "gene_short_name", "sig")])
```
```{r}
#Gene-splicing dynamics

#Assign dynamics

marvel_subset <- IsoSwitch.10x(MarvelObject=marvel_subset,
                        pval.sj=0.05,
                        delta.sj=5,
                        min.gene.norm=1.0,
                        pval.adj.gene=0.05,
                        log2fc.gene=0.5
                        )

marvel_subset$SJ.Gene.Cor$Proportion$Plot
```
```{r}
marvel_subset$SJ.Gene.Cor$Proportion$Table
```
```{r}
head(marvel_subset$SJ.Gene.Cor$Data[,c("coord.intron", "gene_short_name", "cor.complete")])
```
```{r}
#Coordinated
# Define cell groups
    # Retrieve sample metadata
    sample.metadata <- marvel_subset$sample.metadata
    
    # MSS
    index <- which(sample.metadata$cell.type=="cancer cell")
    cell.ids.1 <- sample.metadata[index, "cell.id"]
    length(cell.ids.1)
```

```{r}
    # MSI
    index <- which(sample.metadata$cell.type=="immature enterocyte")
    cell.ids.2 <- sample.metadata[index, "cell.id"]
    length(cell.ids.2)
```
```{r}


    # Save into list
    cell.group.list <- list("cancer cell"=cell.ids.1,
                            "immature enterocyte"=cell.ids.2
                            )
    
# Plot cell groups
marvel_subset <- PlotValues.PCA.CellGroup.10x(MarvelObject=marvel_subset,
                                       cell.group.list=cell.group.list,
                                       legendtitle="Cell group",
                                       type="tsne"
                                       )

plot_group <- marvel_subset$adhocPlot$PCA$CellGroup

# Plot gene expression
marvel_subset <- PlotValues.PCA.Gene.10x(MarvelObject=marvel_subset,
                                  gene_short_name="VIM",
                                  color.gradient=c("grey","cyan","green","yellow","red"),
                                  type="tsne"
                                  )


plot_gene <- marvel_subset$adhocPlot$PCA$Gene

# Plot PSI
marvel_subset <- PlotValues.PCA.PSI.10x(MarvelObject=marvel_subset,
                                 coord.intron="chr10:17235390:17235845",
                                 min.gene.count=3,
                                 log2.transform=FALSE,
                                 color.gradient=c("grey","cyan","green","yellow","red"),
                                 type="tsne"
                                 )
 
plot_sj <- marvel_subset$adhocPlot$PCA$PSI

# Arrange and view plots
grid.arrange(plot_group, plot_gene, plot_sj, nrow=1)
```
```{r}
#Opposing

# Plot gene expression
marvel_subset <- PlotValues.PCA.Gene.10x(MarvelObject=marvel_subset,
                                  gene_short_name="UQCRH",
                                  color.gradient=c("grey","cyan","green","yellow","red"),
                                  type="tsne"
                                  )


plot_gene <- marvel_subset$adhocPlot$PCA$Gene

# Plot PSI
marvel_subset <- PlotValues.PCA.PSI.10x(MarvelObject=marvel_subset,
                                 coord.intron="chr1:46310317:46316551",
                                 min.gene.count=3,
                                 log2.transform=FALSE,
                                 color.gradient=c("grey","cyan","green","yellow","red"),
                                 type="tsne"
                                 )
 
plot_sj <- marvel_subset$adhocPlot$PCA$PSI

# Arrange and view plots
grid.arrange(plot_group, plot_gene, plot_sj, nrow=1)
```
```{r}
#Iso-switch

# Plot gene expression
marvel_subset <- PlotValues.PCA.Gene.10x(MarvelObject=marvel_subset,
                                  gene_short_name="RBM39",
                                  color.gradient=c("grey","cyan","green","yellow","red"),
                                  type="tsne"
                                  )


plot_gene <- marvel_subset$adhocPlot$PCA$Gene

# Plot PSI: SJ-1
marvel_subset <- PlotValues.PCA.PSI.10x(MarvelObject=marvel_subset,
                                 coord.intron="chr20:35740888:35741940",
                                 min.gene.count=3,
                                 log2.transform=FALSE,
                                 color.gradient=c("grey","cyan","green","yellow","red"),
                                 type="tsne"
                                 )
 
plot_sj_1 <- marvel_subset$adhocPlot$PCA$PSI

# Plot PSI: SJ-2
marvel_subset <- PlotValues.PCA.PSI.10x(MarvelObject=marvel_subset,
                                 coord.intron="chr20:35739018:35740823",
                                 min.gene.count=3,
                                 log2.transform=FALSE,
                                 color.gradient=c("grey","cyan","green","yellow","red"),
                                 type="tsne"
                                 )
 
plot_sj_2 <- marvel_subset$adhocPlot$PCA$PSI

# Arrange and view plots
grid.arrange(plot_gene, plot_sj_1, plot_sj_2, nrow=1)
```
```{r}
Complex

# Gene 1
  # Plot gene expression
  marvel_subset <- PlotValues.PCA.Gene.10x(MarvelObject=marvel_subset,
                                    gene_short_name="TPM1",
                                    color.gradient=c("grey","cyan","green","yellow","red"),
                                    type="tsne"
                                    )

  plot.1_gene <- marvel_subset$adhocPlot$PCA$Gene
  
  # Plot PSI: SJ-1
  marvel_subset <- PlotValues.PCA.PSI.10x(MarvelObject=marvel_subset,
                                   coord.intron="chr15:63064143:63065895",
                                   min.gene.count=3,
                                   log2.transform=FALSE,
                                   color.gradient=c("grey","cyan","green","yellow","red"),
                                   type="tsne"
                                   )
   
  plot.1_sj_1 <- marvel_subset$adhocPlot$PCA$PSI
  
  # Plot PSI: SJ-2
  marvel_subset <- PlotValues.PCA.PSI.10x(MarvelObject=marvel_subset,
                                   coord.intron="chr15:63044153:63056984",
                                   min.gene.count=3,
                                   log2.transform=FALSE,
                                   color.gradient=c("grey","cyan","green","yellow","red"),
                                   type="tsne"
                                   )
   
  plot.1_sj_2 <- marvel_subset$adhocPlot$PCA$PSI

# Gene 2
  # Plot gene expression
  marvel_subset <- PlotValues.PCA.Gene.10x(MarvelObject=marvel_subset,
                                    gene_short_name="TPM2",
                                    color.gradient=c("grey","cyan","green","yellow","red"),
                                    type="tsne"
                                    )
  
  
  plot.2_gene <- marvel_subset$adhocPlot$PCA$Gene
  
  # Plot PSI: SJ-1
  marvel_subset <- PlotValues.PCA.PSI.10x(MarvelObject=marvel_subset,
                                   coord.intron="chr9:35684808:35685268",
                                   min.gene.count=3,
                                   log2.transform=FALSE,
                                   color.gradient=c("grey","cyan","green","yellow","red"),
                                   type="tsne"
                                   )
   
  plot.2_sj_1 <- marvel_subset$adhocPlot$PCA$PSI
  
  # Plot PSI: SJ-2
  marvel_subset <- PlotValues.PCA.PSI.10x(MarvelObject=marvel_subset,
                                   coord.intron="chr9:35684551:35685063",
                                   min.gene.count=3,
                                   log2.transform=FALSE,
                                   color.gradient=c("grey","cyan","green","yellow","red"),
                                   type="tsne"
                                   )
   
  plot.2_sj_2 <- marvel_subset$adhocPlot$PCA$PSI
  
# Arrange and view plots
grid.arrange(plot.1_gene, plot.1_sj_1, plot.1_sj_2, 
             plot.2_gene, plot.2_sj_1, plot.2_sj_2,
             nrow=2
             )
```

##Gene ontology analysis
             Gene ontology analysis or pathway enrichment analysis categorises the differentially spliced genes between cancer cells and the others into biological pathways. This may identify sets of genes with similar function or belong to similar biological pathways that are concurrently spliced.
```{r}


marvel_subset <- BioPathways.10x(MarvelObject=marvel_subset,
                          pval=0.05,
                          delta=5,
                          min.gene.norm=1.0,
                          method.adjust="fdr",
                          species="human"
                          )

marvel_subset$DE$BioPathways$Table
```
# Plot pathways
```{r}

go.terms <- c("ATP metabolic process",
              "mitochondrial respiratory chain complex assembly",
              "aerobic respiration",
              "ribose phosphate biosynthetic process",
              "RNA splicing",
              "reactive oxygen species metabolic process",
              "response to mitochondrial depolarisation",
              "intracellular protein transmembrane transport",
              "U2-type prespliceosome assembly",
              "regulation of cell communication by electrical coupling",
              "response to zinc ion"
              )

marvel_subset <- BioPathways.Plot.10x(MarvelObject=marvel_subset,
                               go.terms,
                               y.label.size=8,
                               offset=0.5
                               )

marvel_subset$DE$BioPathways$Plot
```
#Candidate gene analysis

####Define cell groups
  "Our earlier differential analysis included only MSS and MSI. Here, we will include all cell types in this dataset, namely iPSCs, and day-2, -4, and -10 cardiomyocytes.
"
# Retrieve sample metadata
```{r}

sample.metadata <- marvel_subset$sample.metadata

# cancer cell
index <- which(sample.metadata$cell.type=="cancer cell")
cell.ids.1 <- sample.metadata[index, "cell.id"]
length(cell.ids.1)

```
```{r}
# Cardio day 2
index <- which(sample.metadata$cell.type=="immature enterocyte")
cell.ids.2 <- sample.metadata[index, "cell.id"]
length(cell.ids.2)
```
```{r}
# Cardio day 4
index <- which(sample.metadata$cell.type=="fibroblast")
cell.ids.3 <- sample.metadata[index, "cell.id"]
length(cell.ids.3)
```
```{r}
# mature enterocyte
index <- which(sample.metadata$cell.type=="mature enterocyte")
cell.ids.4 <- sample.metadata[index, "cell.id"]
length(cell.ids.4)
```
```{r}
# Save into list
cell.group.list <- list("cancer cell"=cell.ids.1,
                        "immature enterocyte"=cell.ids.2,
                        "fibroblast"=cell.ids.3,
                        "mature enterocyte"=cell.ids.4
                        )
```
```{r}
#Gene expression profiling

marvel <- adhocGene.TabulateExpression.Gene.10x(MarvelObject=marvel,
                                                cell.group.list=cell.group.list,
                                                gene_short_name="PIGR",
                                                min.pct.cells=10,
                                                downsample=TRUE
                                                )

marvel$adhocGene$Expression$Gene$Plot
```
```{r}
marvel$adhocGene$Expression$Gene$Table
```
#SJ usage profiling
```{r}


marvel_subset <- adhocGene.TabulateExpression.PSI.10x(MarvelObject=marvel_subset,
                                               min.pct.cells=10
                                               )

marvel_subset$adhocGene$Expression$PSI$Plot


```
```{r}
head(marvel$adhocGene$Expression$PSI$Table)
```
"Gene-splicing relationship

    Let’s investigate how the top 3 most highly-expressed splice junctions’ usage (SJ-1, -2, and -3) changes relative to TPM2 gene expression changes for all possible pair-wise comparison between iPSCs, and day-2, -4, and -10 cardiomyocytes."

# Perform differential gene expression analysis for all pair-wise group comparison
```{r}
marvel_subset <- adhocGene.DE.Gene.10x(MarvelObject=marvel_subset)
```
# Perform differential splicing expression analysis for all pair-wise group comparison

```{r}
marvel <- adhocGene.DE.PSI.10x(MarvelObject=marvel)
```

# Retrieve SJ DE results table
```{r}

results <- marvel$adhocGene$DE$PSI$Data

# SJ-1
  # Define SJ
  coord.intron <- results[which(results$figure.column=="SJ-1"), "coord.intron"]
  coord.intron <- unique(coord.intron)
  coord.intron
```
```{r}
  # Plotcoord.intron
  marvel <- adhocGene.PlotDEValues.10x(MarvelObject=marvel,
                                       coord.intron=,
                                       log2fc.gene=0.5,
                                       delta.sj=5,
                                       label.size=2,
                                       point.size=2,
                                       xmin=-2.0,
                                       xmax=2.0,
                                       ymin=-25,
                                       ymax=25
                                       )

  plot.1 <- marvel$adhocGene$DE$VolcanoPlot$Plot

# SJ-2
  # Define SJ
  coord.intron <- results[which(results$figure.column=="SJ-2"), "coord.intron"]
  coord.intron <- unique(coord.intron)
  coord.intron
```
```{r}
  # Plot
  marvel <- adhocGene.PlotDEValues.10x(MarvelObject=marvel,
                                       coord.intron=coord.intron,
                                       log2fc.gene=0.5,
                                       delta.sj=5,
                                       label.size=2,
                                       point.size=2,
                                       xmin=-2.0,
                                       xmax=2.0,
                                       ymin=-25,
                                       ymax=25
                                       )
                                         
  plot.2 <- marvel$adhocGene$DE$VolcanoPlot$Plot    

# SJ-3
    # Define SJ
    coord.intron <- results[which(results$figure.column=="SJ-3"), "coord.intron"]
    coord.intron <- unique(coord.intron)
    coord.intron
```
```{r}
    # Plot
    marvel <- adhocGene.PlotDEValues.10x(MarvelObject=marvel,
                                         coord.intron=coord.intron,
                                         log2fc.gene=0.5,
                                         delta.sj=5,
                                         label.size=2,
                                         point.size=2,
                                         xmin=-2.0,
                                         xmax=2.0,
                                         ymin=-25,
                                         ymax=25
                                         )
                                         
    plot.3 <- marvel$adhocGene$DE$VolcanoPlot$Plot    

# Arrange and view plots
grid.arrange(plot.1, plot.2, plot.3,
             nrow=3
             )
```
```{r}
library(wiggleplotr)
#Locate SJ position
  "Locating the position of the splice junctions on the isoforms corresponding to TPM2 will reveal the specific isoforms expressed in our dataset for this."

# SJ-1
    # Define SJs to plot
    coord.intron <- results[which(results$figure.column=="SJ-1"), "coord.intron"]
    coord.intron <- unique(coord.intron)
    coord.intron
```
```{r}
 # Plot
marvel <- adhocGene.PlotSJPosition.10x(MarvelObject=marvel,
                                      coord.intron=coord.intron,
                                      rescale_introns=FALSE,
                                      show.protein.coding.only=TRUE,
                                      anno.label.size=1.5
                                      )

marvel$adhocGene$SJPosition$Plot
  
```
```{r}
# SJ-2
    # Define SJs to plot
    coord.intron <- results[which(results$figure.column=="SJ-2"), "coord.intron"]
    coord.intron <- unique(coord.intron)
    coord.intron
```
```{r}
# Plot
    marvel <- adhocGene.PlotSJPosition.10x(MarvelObject=marvel,
                                          coord.intron=coord.intron,
                                          rescale_introns=FALSE,
                                          show.protein.coding.only=TRUE,
                                          anno.label.size=1.5
                                          )
    
    marvel$adhocGene$SJPosition$Plot
```


